TODO

### 2021-03-17 publications/The_tool_intro/paper.tex
tool_intro: some introduction

	\section{Introduction}
	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
	P4 \cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
describing the data plane layer of packet processing algorithms of different network
devices (e.g. switches, routers) in a protocol and target independent way.

>>>>

	\section{Introduction}
	  Optimization, verification and refactoring are important tasks of a software development process. All of them can be effectively supported by static functional and non-functional (e.g. execution time estimation) analysis. These analysis can be especially interesting in the case of languages having uncommon language constructs or language structures e.g. in the case of some domain specific languages.

	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
	P4~\cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
describing the data plane layer of packet processing algorithms of different network
devices (e.g. switches, routers) in a protocol and target independent way. Figure~\ref{code:P4} illustrates a P4 program. The program first defines the applied header structure, than the parser part describes how the fields of the defined headers will be set from the input bit stream (input packet). Controller part can modify values of fields of headers and metadata by applying lookup tables. The data plane program describes the structure of the tables, the key fields based on that lookups will be executed and the possible results of the lookups, namely the applicable actions. However concrete data of the tables (which actions will be executed with which parameters for which key values) are defined by the control plane program, therefore it will not appear in P4. Finally the deparse part defines how the output bit stream (output packet) will be created from the headers.

	The paper describes an analysis framework for P4. The framework makes possible development of different P4 related analysis methods in a generic and modular way. It uses an internal graph representation where the results of the methods are also represented as part of the graph (mainly by adding new edges to the graph). In this way the methods can use each other's results as well.
